Untitled

### 2017-02-10 Code/plot_age_standardardized_mortality_trends.Rmd
update fig count

**Age-adjusted cancer-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Age-adjusted cardiovascular-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Age-adjusted communicable disease-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Age-adjusted injury-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Age-adjusted non-communicable disease-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Age-adjusted mortality (per 100,000) in males for all other causes, United States, 1969-2013**

@@

**Age-adjusted cancer-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Age-adjusted cardiovascular-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Age-adjusted communicable disease-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Age-adjusted injury-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Age-adjusted non-communicable disease-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Age-adjusted mortality (per 100,000) in females for all other causes, United States, 1969-2013**

>>>>

**Fig S3: Age-adjusted cancer-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Fig S4: Age-adjusted cardiovascular-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Fig S5: Age-adjusted communicable disease-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Fig S6: Age-adjusted injury-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Fig S7: Age-adjusted non-communicable disease-related mortality (per 100,000) in males, United States, 1969-2013**

@@

**Fig S8: Age-adjusted mortality (per 100,000) in males for all other causes, United States, 1969-2013**

@@

**Fig S9: Age-adjusted cancer-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Fig S10: Age-adjusted cardiovascular-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Fig S11: Age-adjusted communicable disease-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Fig S12: Age-adjusted injury-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Fig S13: Age-adjusted non-communicable disease-related mortality (per 100,000) in females, United States, 1969-2013**

@@

**Fig S14: Age-adjusted mortality (per 100,000) in females for all other causes, United States, 1969-2013**
